---
title: "W01_homework_fnh"
author: "Frederik Normann Holm"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mapping ruins in New South Wales using Leaflet

The following assignment attempts to map the coordinates of several ruins in New South Wales 

Firstly i load the necessary packages 
```{r packages}
library(leaflet)
library(tidyverse)
library(dplyr)
```

## Now for the coordinates

in the following section, i will plot the coordinates of the ruins in an interactive map that can be accessed via a browser
first i load the data via 'read.csv()' and print it to check if it worked
i remove the last row from the dataframe because it contains NA's and that interferes with my leaflet plot

```{r read csv}
ruins <- read.csv(file = "data/RCFeature2018.csv")
ruinsdf <- as.data.frame(ruins)
ruinsdf2 <- ruinsdf[-257,]
head(ruinsdf2)
```

Now for mapping the coordinates, i only want the "Latitude" and "Longtitude" columns.
for this i simply write the names of the columns in my lines of code

```{r leaflet map}
ruinsnsw <- leaflet(ruinsdf2) %>%
            addTiles() %>%
            addAwesomeMarkers(lng = ruinsdf2$Longitude, 
                              lat = ruinsdf2$Latitude, 
                              popup = paste("FeatureID:", ruinsdf2$FeatureID, "<br>",
                                            "FeatureType:", ruinsdf2$FeatureType, "<br>",
                                            "Description:", ruinsdf2$Description))
ruinsnsw
```

This is all my head could wrap around for now after struggling to figure out a neat way to include FeatureID, FeatureType and Description for a while

```{r save as html}
library(htmlwidgets)
saveWidget(ruinsnsw, "ruinsnsw.html", selfcontained = TRUE)
```

